The \dealii{} Library, Version 9.0

### 2018-04-07 9.0/paper.tex
Fill out the LinearOperator paragraph.

\item
  Improved support for LinearOperator (Trilinos payload, Schur complement,
  iterative inverse), removal of old wrapper classes

>>>>

\item
  \texttt{LinearOperator}, a flexible template class that implements the action of a
  linear operator (see \cite{MaierBardelloniHeltai-2016-b}), now supports
  computations with Trilinos, Schur complements, and linear constraints. This
  class is, as of this release, the official replacement for about half a dozen
  similar (but less general) classes, such as \texttt{FilteredMatrix},
  \texttt{IterativeInverse}, and \texttt{PointerMatrix}.
